Gene Enrichment Analysis with MSigDB

### 2022-07-27 MSigDB.Rmd
Will be removing Missingness Report and Remapping

---
title: "Gene Enrichment Analysis with MSigDB"
author: "Angela Yoder"
date: "`r Sys.Date()`"
---

@@

```{r, echo = FALSE}
library(msigdbr)

@@

@@

@@

library(biomaRt)
#ensembl_version = "https://ensembl.org"

#ensembl = useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "rnorvegicus_gene_ensembl", version = 109)
ensembl.miss = useEnsembl(biomart="ensembl",dataset = "rnorvegicus_gene_ensembl")
ensembl = useEnsembl(biomart="ensembl",dataset = "rnorvegicus_gene_ensembl", version = 104)

@@

# getting entrez ids
get_entrez = getBM(attributes=c("ensembl_gene_id",
                              "external_gene_name",
                              "description",
                              "chromosome_name",
                              "start_position",
                              "end_position",
                              "gene_biotype",
                            #"entrezgene_trans_name",
                            "entrezgene_id"),
                 filters = 'biotype',
                 values = "protein_coding",
                 mart = ensembl.miss)

@@

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(entrez_brain.1, "EntrezIds_brain.csv")
write.csv(entrez_liver.1, "EntrezIds_liver.csv")

@@

missing.tes.liver = c("ENSRNOG00000020805", "ENSRNOG00000050499", "ENSRNOG00000049727", "ENSRNOG00000033130", "ENSRNOG00000042543", "ENSRNOG00000046529", "ENSRNOG00000013464", "ENSRNOG00000049515", "ENSRNOG00000013410", "ENSRNOG00000016535", "ENSRNOG00000033619", "ENSRNOG00000033245")

@@

Of most concern were the 12 missing Ensembl IDs from the TES protein-coding genes in the liver (34% of total missing). We investigated further and found that these genes are still available in Ensembl databases, under different names.

@@

Additionally, significant target genes brain were found to have a high degree of missingness, with 36% missing.

@@

```{r, echo = FALSE, message = FALSE, warning = FALSE}

@@

# C8

#out.brain_C8 = list(c(), c(), c(), c(), c())
#database = msigdbr_t2g_C8

#for (i in 1:5)
#{
#  vect = brain.list[[i]]
#  entrez = entrez_brain$entrezgene_id[entrez_brain$ensembl_gene_id %in% vect]
#  entrez = na.omit(entrez)
#  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
#  out.brain_C8[[i]] = data.frame(ID = listt$ID, Description = #listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = #listt$geneID)
#}

#out.liver_C8 = list(c(), c(), c(), c(), c())

#for (i in 1:5)
#{
#  vect = liver.list[[i]]
#  entrez = entrez_liver$entrezgene_id[entrez_liver$ensembl_gene_id %in% vect]
#  entrez = na.omit(entrez)
#  listt = enricher(gene = entrez, TERM2GENE = database, pAdjustMethod = "fdr")
#  out.liver_C8[[i]] = data.frame(ID = listt$ID, Description = #listt$Description, pvalue = listt$pvalue, p.adjust = listt$p.adjust, geneID = #listt$geneID)
#}

#first.brain = rbind(out.brain_H[[1]], out.brain_C2[[1]], out.brain_C5[[1]], out.brain_C8[[1]])
#second.brain = rbind(out.brain_H[[2]], out.brain_C2[[2]], out.brain_C5[[2]], out.brain_C8[[2]])
#third.brain = rbind(out.brain_H[[3]], out.brain_C2[[3]], out.brain_C5[[3]], out.brain_C8[[3]])
#fourth.brain = rbind(out.brain_H[[4]], out.brain_C2[[4]], out.brain_C5[[4]], out.brain_C8[[4]])
#fifth.brain = rbind(out.brain_H[[5]], out.brain_C2[[5]], out.brain_C5[[5]], out.brain_C8[[5]])

#first.liver = rbind(out.liver_H[[1]], out.liver_C2[[1]], out.liver_C5[[1]], out.liver_C8[[1]])
#second.liver = rbind(out.liver_H[[2]], out.liver_C2[[2]], out.liver_C5[[2]], out.liver_C8[[2]])
#third.liver = rbind(out.liver_H[[3]], out.liver_C2[[3]], out.liver_C5[[3]], out.liver_C8[[3]])
#fourth.liver = rbind(out.liver_H[[4]], out.liver_C2[[4]], out.liver_C5[[4]], out.liver_C8[[4]])
#fifth.liver = rbind(out.liver_H[[5]], out.liver_C2[[5]], out.liver_C5[[5]], out.liver_C8[[5]])

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
#setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
#write.csv(first.brain, "Brain Enrichment_1.csv")
#write.csv(second.brain, "Brain Enrichment_2.csv")
#write.csv(third.brain, "Brain Enrichment_3.csv")
#write.csv(fourth.brain, "Brain Enrichment_4.csv")
#write.csv(fifth.brain, "Brain Enrichment_5.csv")

#write.csv(first.liver, "liver Enrichment_1.csv")
#write.csv(second.liver, "liver Enrichment_2.csv")
#write.csv(third.liver, "liver Enrichment_3.csv")
#write.csv(fourth.liver, "liver Enrichment_4.csv")
#write.csv(fifth.liver, "liver Enrichment_5.csv")

@@

@@

knitr::kable(out.brain_H[[1]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_H[[2]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_H[[3]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_H[[4]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_H[[5]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_H[[6]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

```{r, echo = FALSE}
# Search KEGG

these_1 = grep("KEGG", out.brain_C2[[1]][,1], value = TRUE)
these_2 = grep("KEGG", out.brain_C2[[2]][,1], value = TRUE)
these_3 = grep("KEGG", out.brain_C2[[3]][,1], value = TRUE)
these_4 = grep("KEGG", out.brain_C2[[4]][,1], value = TRUE)
these_5 = grep("KEGG", out.brain_C2[[5]][,1], value = TRUE)
these_6 = grep("KEGG", out.brain_C2[[6]][,1], value = TRUE)

knitr::kable(out.brain_C2[[1]][out.brain_C2[[1]][,1] %in% these_1,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_C2[[2]][out.brain_C2[[2]][,1] %in% these_2,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_C2[[3]][out.brain_C2[[3]][,1] %in% these_3,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_C2[[4]][out.brain_C2[[4]][,1] %in% these_4,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_C2[[5]][out.brain_C2[[5]][,1] %in% these_5,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C2[[6]][out.brain_C2[[6]][,1] %in% these_6,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

these_1 = grep("GOBP", out.brain_C5[[1]][,1], value = TRUE)
these_2 = grep("GOBP", out.brain_C5[[2]][,1], value = TRUE)
these_3 = grep("GOBP", out.brain_C5[[3]][,1], value = TRUE)
these_4 = grep("GOBP", out.brain_C5[[4]][,1], value = TRUE)
these_5 = grep("GOBP", out.brain_C5[[5]][,1], value = TRUE)
these_6 = grep("GOBP", out.brain_C5[[6]][,1], value = TRUE)

knitr::kable(out.brain_C5[[1]][out.brain_C5[[1]][,1] %in% these_1,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_C5[[2]][out.brain_C5[[2]][,1] %in% these_2,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_C5[[3]][out.brain_C5[[3]][,1] %in% these_3,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002381")
knitr::kable(out.brain_C5[[4]][out.brain_C5[[4]][,1] %in% these_4,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_C5[[5]][out.brain_C5[[5]][,1] %in% these_5,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C5[[6]][out.brain_C5[[6]][,1] %in% these_6,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

@@

```{r, echo = FALSE}
# search KEGG

these_1 = grep("KEGG", out.liver_C2[[1]][,1], value = TRUE)

knitr::kable(out.liver_C2[[1]][out.liver_C2[[1]][,1] %in% these_1,], caption = "C2: KEGG Liver TES Protein-Coding Gene: ENSRNOG00000047481")

@@

these_1 = grep("GOBP", out.liver_C5[[1]][,1], value = TRUE)

knitr::kable(out.liver_C5[[1]][out.liver_C5[[1]][,1] %in% these_1,], caption = "C5: GO Biological Processes Liver TES Protein-Coding Gene: ENSRNOG00000047481")

>>>>

---
title: "Gene Enrichment Analysis with MSigDB"
author: "Angela Yoder"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

@@

```{r}
library(msigdbr)

@@

```{r}

@@

summ.brain = fix.read.csv(summ.brain)
summ.liver = fix.read.csv(summ.liver)

@@

library(biomaRt)

#ensembl = useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "rnorvegicus_gene_ensembl", version = 109)
ensembl = useEnsembl(biomart="ensembl",dataset = "rnorvegicus_gene_ensembl")
ensembl = useEnsembl(biomart="ensembl",dataset = "rnorvegicus_gene_ensembl", version = 104)

@@

# getting entrez ids
get_entrez = getBM(attributes=c("ensembl_gene_id",
                              "external_gene_name",
                              "description",
                              "chromosome_name",
                              "start_position",
                              "end_position",
                              "gene_biotype",
                            #"entrezgene_trans_name",
                            "entrezgene_id"),
                 filters = 'biotype',
                 values = "protein_coding",
                 mart = ensembl)

@@

entrez_topbrain = get_entrez[get_entrez$ensembl_gene_id %in% top.brain$Gene_symbol,]
entrez_topliver = get_entrez[get_entrez$ensembl_gene_id %in% top.liver$Gene_symbol,]

@@

#setwd("C:/Users/angel/OneDrive/Desktop/Saba Lab/Data/")
setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
write.csv(entrez_topbrain, "EntrezIds_topbrain.csv")
write.csv(entrez_topliver, "EntrezIds_topliver.csv")
write.csv(entrez_brain.1, "EntrezIds_brain.csv")
write.csv(entrez_liver.1, "EntrezIds_liver.csv")

@@

#missing.tes.liver = c("ENSRNOG00000020805", "ENSRNOG00000050499", "ENSRNOG00000049727", "ENSRNOG00000033130", "ENSRNOG00000042543", "ENSRNOG00000046529", "ENSRNOG00000013464", "ENSRNOG00000049515", "ENSRNOG00000013410", "ENSRNOG00000016535", "ENSRNOG00000033619", "ENSRNOG00000033245")

@@

@@

## Remapping Missing Ensembl IDs

Due to this missingness, efforts were made to identify new Ensembl IDs for these missing genes. Updated Ensembl IDs for the missing IDs were retrieved via Ensembl.org's ID History Converter, whose output was subsetted by updates to Version 105. A decent portion of our missing Ensembl IDs had corresponding IDs in the new version, however, many were divided into multiple IDs. These were not able to be converted one-to-one due to uncertainty about which version of the new IDs our detected genes would map to. This resulted in only one target gene from the brain and one target gene from the liver having a viable one-to-one match to a Version 105 Ensembl ID.

```{r}

## we got this from http://uswest.ensembl.org/Rattus_norvegicus/Tools/IDMapper?db=core;expand_form=true;tl=veVyFBLEW339Hw8k-8445349

remap.tesbrain = read.csv("remapping_TESbrain.csv")
remap.tesliver = read.csv("remapping_TESliver.csv")
remap.targetbrain = read.csv("remapping_targetbrain.csv")
remap.targetliver = read.csv("remapping_targetliver.csv")

remap.tesbrain$Releases = sub("\\:.*", "", remap.tesbrain$Releases)
remap.targetbrain$Releases = sub("\\:.*", "", remap.targetbrain$Releases)
remap.tesliver$Releases = sub("\\:.*", "", remap.tesliver$Releases)
remap.targetliver$Releases = sub("\\:.*", "", remap.targetliver$Releases)

remap.tesbrain.105 = remap.tesbrain[remap.tesbrain$Releases == 105, ]
remap.targetbrain.105 = remap.targetbrain[remap.targetbrain$Releases == 105, ]
remap.tesliver.105 = remap.tesliver[remap.tesliver$Releases == 105, ]
remap.targetliver.105 = remap.targetliver[remap.targetliver$Releases == 105, ]

```{r}

# summary

summ.remap = data.frame(dataset = missingness$dataset, total.genes = missingness$total, missing.genes = missingness$missing, num.remapped = c(nrow(remap.tesbrain.105), nrow(remap.targetbrain.105), nrow(remap.tesliver.105), nrow(remap.targetliver.105)), num.unique.remapped = c(length(unique(remap.tesbrain.105$Requested.ID)), length(unique(remap.targetbrain.105$Requested.ID)), length(unique(remap.tesliver.105$Requested.ID)), length(unique(remap.targetliver.105$Requested.ID))))

#knitr::kable(summ.remap)

```{r}

# usable remapping

only.one = function(x)
{
  out = c()
  for (i in 1:length(x))
  {
    if (x[i] %in% x[-i])
    {
      out = out
    }
    else
    {
      out = c(out, x[i])
    }
  }
  return(out)
}

usable.tesbrain = remap.tesbrain.105[remap.tesbrain.105$Requested.ID %in% only.one(remap.tesbrain.105$Requested.ID),]
usable.targetbrain = remap.targetbrain.105[remap.targetbrain.105$Requested.ID %in% only.one(remap.targetbrain.105$Requested.ID),]
usable.tesliver = remap.tesliver.105[remap.tesliver.105$Requested.ID %in% only.one(remap.tesliver.105$Requested.ID), ]
usable.targetliver = remap.targetliver.105[remap.targetliver.105$Requested.ID %in% only.one(remap.targetliver.105$Requested.ID),]

one.to.one.match = c(length(usable.tesbrain$Requested.ID), length(usable.targetbrain$Requested.ID), length(usable.tesliver$Requested.ID), length(usable.targetliver$Requested.ID))

summ.remap = data.frame(summ.remap, one.to.one.match)

knitr::kable(summ.remap)

# getting entrez IDs for these Ensembl IDs
# replace ensembl in combine brain and then rerun

replace.id = function(final, replace)
{
  for(i in 1:length(replace$Requested.ID))
  {
    final[final == replace$Requested.ID[i]] = replace$Matched.ID.s[i]
  }
  return(final)
}

combine.brain.remap = replace.id(combine.brain, usable.targetbrain)
combine.liver.remap = replace.id(combine.liver, usable.targetliver)

# run biomart to get entrez IDS

library(biomaRt)

ensembl = useEnsembl(biomart="ensembl",dataset = "rnorvegicus_gene_ensembl")

get_entrez = getBM(attributes=c("ensembl_gene_id",
                              "external_gene_name",
                              "description",
                              "chromosome_name",
                              "start_position",
                              "end_position",
                              "gene_biotype",
                            #"entrezgene_trans_name",
                            "entrezgene_id"),
                 filters = 'biotype',
                 values = "protein_coding",
                 mart = ensembl)

# compare to other dataframe

setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
entrez_brain = read.csv("EntrezIds_brain.csv")
entrez_liver = read.csv("EntrezIds_liver.csv")

@@

Summary of enrichment analysis was complicated by the R function enricher not including fold enrichment in its output. I have included a summary table of the number of enriched terms for each top TES protein-coding gene in this analysis. At the end of the document, there are also plots provided in the r package enrichplot, though they would only correspond to a single TES protein-coding gene's analysis within a single gene set. I am unsure how useful they would be in describing these relationships.

```{r, message = FALSE, warning = FALSE}

@@

```{r}
# looking for correlations to TES also

setwd("C:/Users/yodeange/OneDrive - The University of Colorado Denver/Saba Lab/Data")
entrez_topbrain = read.csv("EntrezIds_topbrain.csv")
entrez_topliver = read.csv("EntrezIds_topliver.csv")

database = msigdbr_t2g_H
two.H = enricher(gene = c(entrez_topbrain$entrezgene_id[2], 315323, 171154), TERM2GENE = database, pAdjustMethod = "fdr")
#two.H$geneID

five.H1 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[5], 50549, 84029, 25598, 29171)), TERM2GENE = database, pAdjustMethod = "fdr")
#five.H1$geneID

five.H2 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[5], 266708, 29187, 309178, 171371)), TERM2GENE = database, pAdjustMethod = "fdr")
#five.H2$geneID

database = msigdbr_t2g_C2
five.c2 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[5], 50549, 25598, 29171)), TERM2GENE = database, pAdjustMethod = "fdr")
#five.c2$geneID

six.c2 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[6], 291283, 307092, 289533, 63867)), TERM2GENE = database, pAdjustMethod = "fdr")
#six.c2$geneID

database = msigdbr_t2g_C5
one.c5 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[1], 296366, 312102, 301229, 289057)), TERM2GENE = database, pAdjustMethod = "fdr")
#one.c5$geneID

two.c5 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[2], 29300, 117033, 25098)), TERM2GENE = database, pAdjustMethod = "fdr")
#two.c5$geneID
# "311862/117033"

three.c5 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[3], 24833, 408236, 81806, 171154)), TERM2GENE = database, pAdjustMethod = "fdr")
#three.c5$geneID

six.c5 = enricher(gene = c(c(entrez_topbrain$entrezgene_id[6], 291283, 311387, 307092)), TERM2GENE = database, pAdjustMethod = "fdr")
#six.c5$geneID

database = msigdbr_t2g_H
liver.H = enricher(gene = c(c(entrez_topliver$entrezgene_id, 24294, 689619, 79208, 29471, 24898, 25412, 25546, 25041, 29361)), TERM2GENE = database, pAdjustMethod = "fdr")
#liver.H$geneID

################# LOOK INTO THIS ONE #####################
database = msigdbr_t2g_C2
liver.c2 = enricher(gene = c(c(entrez_topliver$entrezgene_id, 65187, 24409, 289606, 25153, 24182, 24410, 140675, 25033, 29595, 116506, 24316, 81721, 24922, 29471, 25674, 24418, 29234, 170796, 25041)), TERM2GENE = database, pAdjustMethod = "fdr")
#liver.c2$geneID

database = msigdbr_t2g_C5
liver.c5 = enricher(gene = c(c(entrez_topliver$entrezgene_id, 65187, 24409, 689043, 289606, 114032, 60337, 50599, 170899, 24410, 140675, 117018, 307206, 24316, 81721, 24922, 29161, 294388, 29701, 25674, 170739, 24602, 78956, 24418, 307540, 25041)), TERM2GENE = database, pAdjustMethod = "fdr")
#liver.c5$geneID

@@

```{r}

hallmark.brain = c(nrow(out.brain_H[[1]]), nrow(out.brain_H[[2]]), nrow(out.brain_H[[3]]), nrow(out.brain_H[[4]]), nrow(out.brain_H[[5]]), nrow(out.brain_H[[6]]))

these_1k = grep("KEGG", out.brain_C2[[1]][,1], value = TRUE)
these_2k = grep("KEGG", out.brain_C2[[2]][,1], value = TRUE)
these_3k = grep("KEGG", out.brain_C2[[3]][,1], value = TRUE)
these_4k = grep("KEGG", out.brain_C2[[4]][,1], value = TRUE)
these_5k = grep("KEGG", out.brain_C2[[5]][,1], value = TRUE)
these_6k = grep("KEGG", out.brain_C2[[6]][,1], value = TRUE)

kegg.brain = c(nrow(out.brain_C2[[1]][out.brain_C2[[1]][,1] %in% these_1k,]), 
               nrow(out.brain_C2[[2]][out.brain_C2[[2]][,1] %in% these_2k,]), 
               nrow(out.brain_C2[[3]][out.brain_C2[[3]][,1] %in% these_3k,]), 
               nrow(out.brain_C2[[4]][out.brain_C2[[4]][,1] %in% these_4k,]), 
               nrow(out.brain_C2[[5]][out.brain_C2[[5]][,1] %in% these_5k,]), 
               nrow(out.brain_C2[[6]][out.brain_C2[[6]][,1] %in% these_6k,]))

these_1g = grep("GOBP", out.brain_C5[[1]][,1], value = TRUE)
these_2g = grep("GOBP", out.brain_C5[[2]][,1], value = TRUE)
these_3g = grep("GOBP", out.brain_C5[[3]][,1], value = TRUE)
these_4g = grep("GOBP", out.brain_C5[[4]][,1], value = TRUE)
these_5g = grep("GOBP", out.brain_C5[[5]][,1], value = TRUE)
these_6g = grep("GOBP", out.brain_C5[[6]][,1], value = TRUE)

go.brain = c(nrow(out.brain_C5[[1]][out.brain_C5[[1]][,1] %in% these_1g,]), 
               nrow(out.brain_C5[[2]][out.brain_C5[[2]][,1] %in% these_2g,]), 
               nrow(out.brain_C5[[3]][out.brain_C5[[3]][,1] %in% these_3g,]), 
               nrow(out.brain_C5[[4]][out.brain_C5[[4]][,1] %in% these_4g,]), 
               nrow(out.brain_C5[[5]][out.brain_C5[[5]][,1] %in% these_5g,]), 
               nrow(out.brain_C5[[6]][out.brain_C5[[6]][,1] %in% these_6g,]))

summary.brain = data.frame(gene.symbol = summ.brain$Gene_Symbol, hallmark.terms = hallmark.brain, kegg.terms = kegg.brain, go.bio.process.terms = go.brain, sig.target.genes = summ.brain$Number_Target_Genes)

knitr::kable(summary.brain, caption = "Number of Significant Terms for Each Top Brain TES Protein-Coding Genes")

@@

```{r}

#knitr::kable(out.brain_H[[1]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_H[[2]], caption = "2. Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002548")
#knitr::kable(out.brain_H[[3]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000002381")
#knitr::kable(out.brain_H[[4]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_H[[5]], caption = "5. Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000059507")
#knitr::kable(out.brain_H[[6]], caption = "Hallmark Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

```{r}
# Search KEGG

#knitr::kable(out.brain_C2[[1]][out.brain_C2[[1]][,1] %in% these_1k,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000005652")
#knitr::kable(out.brain_C2[[2]][out.brain_C2[[2]][,1] %in% these_2k,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002548")
#knitr::kable(out.brain_C2[[3]][out.brain_C2[[3]][,1] %in% these_3k,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000002381")
#knitr::kable(out.brain_C2[[4]][out.brain_C2[[4]][,1] %in% these_4k,], caption = "C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000003845")
knitr::kable(out.brain_C2[[5]][out.brain_C2[[5]][,1] %in% these_5k,], caption = "5. C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C2[[6]][out.brain_C2[[6]][,1] %in% these_6k,], caption = "6. C2: KEGG Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

```{r}

knitr::kable(out.brain_C5[[1]][out.brain_C5[[1]][,1] %in% these_1g,], caption = "1. C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000005652")
knitr::kable(out.brain_C5[[2]][out.brain_C5[[2]][,1] %in% these_2g,], caption = "2. C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002548")
knitr::kable(out.brain_C5[[3]][out.brain_C5[[3]][,1] %in% these_3g,], caption = "3. C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000002381")
#knitr::kable(out.brain_C5[[4]][out.brain_C5[[4]][,1] %in% these_4g,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000003845")
#knitr::kable(out.brain_C5[[5]][out.brain_C5[[5]][,1] %in% these_5g,], caption = "C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000059507")
knitr::kable(out.brain_C5[[6]][out.brain_C5[[6]][,1] %in% these_6g,], caption = "6. C5: GO Biological Process Brain TES Protein-Coding Gene: ENSRNOG00000000010")

@@

```{r}

hallmark.liver = nrow(out.liver_H[[1]])

these_1k = grep("KEGG", out.liver_C2[[1]][,1], value = TRUE)
kegg.liver = nrow(out.liver_C2[[1]][out.liver_C2[[1]][,1] %in% these_1k,])

these_1g = grep("GOBP", out.liver_C5[[1]][,1], value = TRUE)
go.liver = nrow(out.liver_C5[[1]][out.liver_C5[[1]][,1] %in% these_1g,])

summary.liver = data.frame(gene.symbol = summ.liver$Gene_Symbol, hallmark.terms = hallmark.liver, kegg.terms = kegg.liver, go.bio.process.terms = go.liver, sig.target.genes = summ.liver$Number_Target_Genes)

knitr::kable(summary.liver, caption = "Number of Significant Terms for Each Top Liver TES Protein-Coding Genes")

@@

```{r}
# search KEGG

knitr::kable(out.liver_C2[[1]][out.liver_C2[[1]][,1] %in% these_1k,], caption = "C2: KEGG Liver TES Protein-Coding Gene: ENSRNOG00000047481")

@@

```{r}

knitr::kable(out.liver_C5[[1]][out.liver_C5[[1]][,1] %in% these_1g,], caption = "C5: GO Biological Processes Liver TES Protein-Coding Gene: ENSRNOG00000047481")

### Other Plots

```{r}

library(enrichplot)
barplot(listt)
cnetplot(listt) 
dotplot(listt)
#goplot(listt) #DAG
